Sequential Composition for Relaxed Memory: Pomsets with Predicate Transformers

### 2021-07-08 paper/tool.tex
Remove duplication between C11 and Tool sections

\PwTer{} allows several modes of evaluation: it can evaluate the rules of Fig.~\ref{fig:seq}, implementing \PwT; it can generate program order according to Section~\ref{sec:c11}, implementing \PwTpo; and similar to \MRD~\cite{DBLP:conf/esop/PaviottiCPWOB20}, it can construct C11-style pre-executions and filter them according to the rules of C11.
Our choice of C11 rules is careful: we take the rules of RC11~\cite{DBLP:conf/pldi/LahavVKHD17}, but we replace the overly strong No-Thin-Air restriction $\text{acyclic}(\rrf\cup\rpox)$ with $\text{acyclic}(\rrf\cup\lt)$. 
This is a more precise categorisation of thin-air behavior, and it allows aggressive compiler optimizations which would be erroneously forbidden by RC11's original No-Thin-Air axiom.
We show \PwTer{} in action in Fig.~\ref{fig:tool}.
Finally, \PwTer{} also allows us to toggle the complete check of~\ref{def:pomset}, providing an interface for understanding how fragments of code might compose by exposing preconditions and termination conditions which are not yet tautologies.

>>>>

\PwTer{} allows several modes of evaluation: it can evaluate the rules of Fig.~\ref{fig:seq}, implementing \PwT; it can generate program order according to \textsection~\ref{sec:c11}, implementing \PwTpo; and similar to \MRD~\cite{DBLP:conf/esop/PaviottiCPWOB20}, it can construct C11-style pre-executions and filter them according to the rules of \rcXI{} as described in \textsection\ref{sec:c11}.
Finally, \PwTer{} also allows us to toggle the complete check of~\ref{def:complete}, providing an interface for understanding how fragments of code might compose by exposing preconditions and termination conditions that are not yet tautologies.
We show \PwTer{} in action in Fig.~\ref{fig:tool}. 
\PwTer{} will be made open source upon publication.
%\PwTer{} is available online at \url{https://github.com/graymalkin/pomsets-with-predicate-transformers}.
